Diagnosing Child Poverty Reduction Interventions

### 2024-09-04 minos/outcomes/CPR_Intervention_Diagnostics.Rmd
Fixing some typos in CPR Intervention Diagnostics script

int.inc <- int %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

@@

int.inc <- int %>%
  select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
  mutate(nkids_any = (nkids > 0)) %>%
  filter(nkids_any = TRUE) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

@@

  filtered_combined <- combined %>%
    filter(hh_income > lower_cutoff, hh_income < upper_cutoff)

  p <- ggplot(filtered_combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
    geom_density_ridges() +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))
  return(p)
}

>>>>

int.inc <- int.dat %>%
  select(pidp, hidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income,w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

@@

int.inc <- int.dat %>%
  select(pidp, hidp, time, hh_income, age, nkids, weight) %>%
  mutate(nkids_any = (nkids > 0)) %>%
  filter(nkids_any = TRUE) %>%
  group_by(time) %>%
  summarise(hh_income = weighted.mean(x = hh_income, w = weight, na.rm = TRUE)) %>%
  mutate(scen = 'Intervention')

@@

  #filtered_combined <- combined %>%
  #  filter(hh_income > lower_cutoff, hh_income < upper_cutoff)

  p <- ggplot(combined, aes(x = hh_income, y = time, group = interaction(time, Source), color = Source)) +
    geom_density_ridges() +
    labs(title = 'Household Income Density Plots',
         subtitle = paste0('Quintile ', quintile))
  return(p)
}
